Unimodular covers of 3-dimensional parallelepipeds and Cayley sums

### 2019-07-12 unimodular-covers.tex
adding  some questions

\begin{definition}
In the above conditions, we say that $Q$ \emph{is nef for $P$} if the normal fan of $Q$ refines that of $P$. If this happens, we say that $\cayley(P,Q)$ is a \emph{nef Cayley sum}.

@@

The so-called \emph{Cayley Trick} is the isomorphism
\[
2\cayley(P, Q) \cap (\R^d\times \{1\}) \cong P+Q,
\]
which induces the following canonical bijections:
\begin{align*}
\text{polyhedral subdivisions of $\cayley(P,Q)$} &\leftrightarrow \text{mixed subdivisions of $P + Q$}\\
\text{triangulations of $\cayley(P,Q)$} &\leftrightarrow \text{fine mixed subdivisions of $P + Q$}\\
\text{unimodular simplices in $\cayley(P,Q)$} &\leftrightarrow \text{unimodular prod-simplices in $P + Q$}.
\end{align*}
See \cite{DLRS2010} for more details on the Cayley Trick and on triangulations and polyhedral subdivisions of polytopes.
In fact these bijections can be taken as definitions of the objects in the right-hand sides. In particular, 
we call \emph{prod-simplices} in $P+Q$ the Minkowski sums $T_1+T_2$ where $T_1\subset P$ and $T_2\subset Q$ are simplices with complementary affine spans. A prod-simplex is \emph{unimodular} if the edge vectors from a vertex of $T_1$ and from a vertex of $T_2$ form a unimodular basis.

@@

\begin{figure}
\includegraphics[scale=.3]{setup.png}
\caption{Setup for \Cref{lemma:cayley}}
\end{figure}

>>>>

\begin{definition}
In the above conditions, we say that $Q$ \emph{is a weak Minkowski summand of $P$} if the normal fan of $Q$ refines that of $P$. 
If this happens, we say that $\cayley(P,Q)$ is a \emph{nef Cayley sum}.\giulia{I guess there's no nice term for this now...}

@@

The so-called \emph{Cayley Trick} is the isomorphism
\[
2\cayley(P, Q) \cap (\R^d\times \{1\}) \cong P+Q,
\]
which induces the following canonical bijections:

\begin{center}
  \begin{tabular}{ c | c }
    $\cayley(P,Q)$ & $P+Q$\\
    \hline
   polyhedral subdivisions & mixed subdivisions \\
    triangulations & fine mixed subdivisions \\
   unimodular simplices & unimodular prod-simplices \\
  \end{tabular}
\end{center}\giulia{not sure if the table makes it clear that these are bijections}

\begin{align*}
\text{polyhedral subdivisions of $\cayley(P,Q)$} &\leftrightarrow \text{mixed subdivisions of $P + Q$}\\
\text{triangulations of $\cayley(P,Q)$} &\leftrightarrow \text{fine mixed subdivisions of $P + Q$}\\
\text{unimodular simplices in $\cayley(P,Q)$} &\leftrightarrow \text{unimodular prod-simplices in $P + Q$}.
\end{align*}
See \cite{DLRS2010} for more details on the Cayley Trick and on triangulations and polyhedral subdivisions of polytopes.
In fact these bijections can be taken as definitions of the objects in the right-hand sides. In particular, 
we call \emph{prod-simplices} in $P+Q$ the Minkowski sums $T_1+T_2$ where $T_1\subset P$ and $T_2\subset Q$ are simplices with complementary affine spans. A prod-simplex is \emph{unimodular} if the edge vectors from a vertex of $T_1$ and from a vertex of $T_2$ form a unimodular basis.

@@

\begin{figure}
\includegraphics[scale=.3]{setup'.png}
\caption{Setup for \Cref{lemma:cayley}}
\end{figure}
